Simulation Results

### 2020-05-04 HMC Talk Notes.Rmd
ppp monday work computer

---
title: "HMC Talk Notes"
author: "Evan Miyakawa"
date: "4/7/2020"
output: pdf_document
---

@@

>>>>

---
title: "HMC Talk Notes"
author: "Evan Miyakawa"
output: pdf_document
---

@@

## New Notes 5-4-2020

- Might want to include Hamiltonian equations to explain kinetic and potential energy when then giving the visual illustration
- Potential energy is specified by the problem, but kinetic energy is not
- Good illustration might be the project up/down at 36:00 in video

## Old notes

### 2020-05-04 PPP/Figures.Rmd
ppp monday work computer

log_df <- tibble(x = seq(-4,4,length.out = 100), d_norm = - dnorm(x))

log_df %>% ggplot(aes(x,d_norm)) + 
  geom_line(size = 2) + 
  theme_minimal() + 
  theme(
    axis.title = element_blank(),
    axis.text = element_blank()
  )

>>>>

log_df <- tibble(x = seq(-4,4,length.out = 100), d_norm = dnorm(x), log_d_norm =  - log(d_norm))

log_df %>% ggplot(aes(x,log_d_norm)) + 
  geom_line(size = 2) + 
  theme_minimal() + 
  theme(
    axis.title = element_blank(),
    axis.text = element_blank()
  )

### 2020-05-04 Simulation Results/Simulation Results.Rmd
ppp monday work computer

```{r}
bench_results_indiv <- readRDS("bench_results_indiv2.RDS")

bench_results_indiv %>%
  ggplot(aes(x = method, y = time)) +
  geom_boxplot(aes(color = method), coef = 2, outlier.size = 0.75) +
  # geom_boxplot(aes(color = method)) +
  # coord_flip() +
  ylim(0,90) +
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan", "Nimble", "Greta", "Stan Compile")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  xlab("Implementation") + 
  ylab("Completion Time") + 
  ggtitle("Implementation Completion Time Boxplots")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  filter(method %in% c("JAGS", "Nimble", "OpenBUGS", "Stan")) %>% 
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

@@

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(TVD_Ratio)) + 
    geom_histogram(aes(fill = method)) + 
    facet_wrap(facets = "method") + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5)) + 
  ggtitle("Implementation TVD Accuracy Histograms") + 
  xlab("Implementation") + 
  ylab("TVD Ratio")

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(x = method, y = TVD_Ratio)) + 
    geom_boxplot(aes(color = method)) + 
  ggtitle("Implementation TVD Accuracy Boxplots") + 
  xlab("Implementation") + 
  ylab("TVD Ratio") + 
  scale_x_discrete(limits = c("OpenBUGS", "JAGS", "Nimble", "Stan", "Greta")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5))

>>>>

```{r}
bench_results_indiv <- readRDS(here("bench_results_indiv2.RDS"))

bench_results_indiv %>%
  ggplot(aes(x = method, y = time)) +
  geom_boxplot(aes(color = method), coef = 2, outlier.size = 0.75, size = 0.7) +
  # geom_boxplot(aes(color = method)) +
  # coord_flip() +
  ylim(0,90) +
  scale_x_discrete(limits = c("JAGS", "OpenBUGS", "Stan", "Nimble", "Greta", "Stan Compile")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  xlab("Implementation") + 
  ylab("Completion Time") + 
  ggtitle("Implementation Completion Time Boxplots")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

bench_results_indiv %>%
  filter(method %in% c("JAGS", "Nimble", "OpenBUGS", "Stan")) %>% 
  ggplot(aes(time, fill = method)) +
  geom_histogram(aes(y = stat(density)), bins = 20) + 
  # xlim(0,100) +
  facet_wrap(vars(method)) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  ggtitle("Implementation Completion Time Histograms") + 
  xlab("Completion Time") + 
  ylab("Count Density")

@@

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(TVD_Ratio)) + 
    geom_histogram(aes(fill = method)) + 
    facet_wrap(facets = "method") + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20)) + 
  ggtitle("Implementation TVD Accuracy Histograms") + 
  xlab("Implementation") + 
  ylab("TVD Ratio")

time_results %>% 
  pivot_longer(
    # cols = c(jags_dist, bugs_dist, stan_dist, greta_dist, nimble_dist), 
    cols = c(JAGS, OpenBUGS, Stan, Nimble, Greta), 
    names_to = "method",
    values_to = "TVD_Ratio"
  ) %>% 
  ggplot(aes(x = method, y = TVD_Ratio)) + 
    geom_boxplot(aes(color = method), size = 0.7) + 
  ggtitle("Implementation TVD Accuracy Boxplots") + 
  xlab("Implementation") + 
  ylab("TVD Ratio") + 
  scale_x_discrete(limits = c("OpenBUGS", "JAGS", "Nimble", "Stan", "Greta")) + 
  theme(legend.position="none",
        plot.title = element_text(hjust = 0.5),
        text = element_text(size=20))
